The Effect of Events on Australian Parliamentary Discussion (1851--2017)

### 2018-10-03 outputs/docs/events/svm-rmarkdown-article-example.tex
Clean up events paper

\title{The Effect of Events on Australian Parliamentary Discussion (1870--2017) \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris
Cochrane for their helpful suggestions. \textbf{Version as of}: 02
October 2018; \textbf{comments welcome}:
\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}.}  }

@@

\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Monica Alexander (University of Toronto) and Rohan Alexander (Australian National University)},
             pdfkeywords = {text analysis, politics, Australia},  
            pdftitle={The Effect of Events on Australian Parliamentary Discussion (1870--2017)},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

\noindent We systematically analyse how parliamentary discussion changes in
response to different types of events in Australian history. We first
compile a dataset of what was said in Australian state and federal
parliaments from the mid-1800s through to 2017 based on available public
records. We then use a structural text model to reduce the
dimensionality of the text and to impose prior knowledge such as
correlation between days and steady changes over time. Finally, we
consider various events using Bayesian regression with a
Dirichlet-distributed response variable. We find that: 1) elections are
associated with topic changes only when the party in power changes; 2) a
change in government can be associated with topic changes even if the
party in power does not change; 3) economic events, such as financial
crises, have less significant and persistent effects than other events
such as terrorist attacks. Our findings have implications for how we
think about the longer-term trajectory of government policy as the media
cycle becomes increasingly focused on short-term events.

@@

In this paper we examine text records of what was said in Australian
state and federal parliaments from the mid-1800s through to 2017. We use
the Structural Topic Model (STM) of \citet{RobertsStewartAiroldi2016}
for dimensionality reduction and to impose structure such as correlation
between days and changes over time. We then use a simple discrete choice
model to examine changes at various types of events, including: changes
in government; changes in the political environment (as defined by
polling or other results); changes in economic conditions; and other
significant events (such as the 9/11 attacks or the Bali bombings).

@@

Our paper applies a topic model to a dataset of larger-scale
parliamentary text records from multiple Australian parliaments. Our use
of a discrete choice model - essentially a time series multinomial model
of choices - allows us to construct a counterfactual. Our work fits into
a growing literature that considers text as an input to more usual
quantitative techniques, rather than requiring separate analysis. While
using text as data has well-known shortcomings, it allows larger-scale
analysis that would not be viable using less-automated approaches and so
it can identify patterns that may otherwise be overlooked.

@@

Australian parliaments generally make their daily Hansard records
available online as PDFs and these are considered the official release.
Additionally, there is a more limited set of XML records available in
some cases.\footnote{Tim Sherratt makes these XML records available as a
  single download and also presents them in a website
  (\url{http://historichansard.net/}) that can be used to explore
  Commonwealth Hansard records from 1901 to 1980. Commonwealth XML
  records from 1998 to 2014 are available from Andrew Turpin's website,
  and from 2006 through to today from Open Australia's website. The
  records can also be downloaded from the Australian Hansard website.}
We detail the sources of our Hansard PDFs in \ref{hansardsources} and
Appendix \ref{examplehansardpage} provides an example of what a Hansard
PDF looks like. There are 65,000 \textbf{{[}UPDATE{]}} days worth of
publicly available Hansard records across the state and federal
parliaments (Table \ref{tab:yearsusedtable}). Our data cleaning process
indicates concerns with a small number of PDFs and these are detailed in
Appendix \ref{knownhansardissues}.

@@

\caption{\label{tab:missingdays}Missing days}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{rrrrr}
\toprule
year & HoR PDFs                      & Senate sitting days           & HoR sitting days              & HoR difference\\
\midrule
1902 & 106 & 93 & 107 & 1\\
1908 & 93 & 84 & 91 & -2\\
1909 & 97 & 71 & 98 & 1\\
1918 & 87 & 68 & 86 & -1\\
1920 & 113 & 76 & 114 & 1\\
\addlinespace
1921 & 92 & 79 & 93 & 1\\
1934 & 36 & 22 & 35 & -1\\
1935 & 54 & 37 & 55 & 1\\
1942 & 44 & 36 & 45 & 1\\
1948 & 89 & 39 & 90 & 1\\
\addlinespace
1951 & 55 & 40 & 56 & 1\\
1955 & 53 & 36 & 52 & -1\\
1974 & 64 & 64 & 62 & -2\\
1985 & 65 & 74 & 66 & 1\\
1991 & 66 & 83 & 67 & 1\\
\addlinespace
1992 & 60 & 76 & 44 & -16\\
1993 & 47 & 53 & 46 & -1\\
1994 & 69 & 80 & 68 & -1\\
1995 & 71 & 78 & 70 & -1\\
1997 & 79 & 82 & 76 & -3\\
\addlinespace
1998 & 56 & 57 & 54 & -2\\
2000 & 71 & 71 & 73 & 2\\
2002 & 68 & 60 & 69 & 1\\
2003 & 74 & 64 & 75 & 1\\
2004 & 58 & 49 & 59 & 1\\
2012 & 63 & 57 & 67 & 4\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:governments}Change in governments}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{llllll}
\toprule
government & primeMinister & party & start & end & diedInOffice\\
\midrule
Barton & Edmund Barton & Protectionist & 1901-01-01 & 1903-09-24 & No\\
Deakin 1 & Alfred Deakin & Protectionist & 1903-09-24 & 1904-04-27 & No\\
Watson & Chris Watson & Labour & 1904-04-27 & 1904-08-18 & No\\
Reid & George Reid & Free Trade & 1904-08-18 & 1905-07-05 & No\\
Deakin 2 & Alfred Deakin & Protectionist & 1905-07-05 & 1908-11-13 & No\\
\addlinespace
Fisher 1 & Andrew Fisher & Labour & 1908-11-13 & 1909-06-02 & No\\
Deakin 3 & Alfred Deakin & Commonwealth Liberal & 1909-06-02 & 1910-04-29 & No\\
Fisher 2 & Andrew Fisher & Labor & 1910-04-29 & 1913-06-24 & No\\
Cook & Joseph Cook & Commonwealth Liberal & 1913-06-24 & 1914-09-17 & No\\
Fisher 3 & Andrew Fisher & Labor & 1914-09-17 & 1915-10-27 & No\\
\addlinespace
Hughes & Billy Hughes & Labor, National Labor and Nationalist & 1915-10-27 & 1923-02-09 & No\\
Bruce & Stanley Bruce & Nationalist (Coalition) & 1923-02-09 & 1929-10-22 & No\\
Scullin & James Scullin & Labor & 1929-10-22 & 1932-01-06 & No\\
Lyons & Joseph Lyons & United Australia (Coalition) & 1932-01-06 & 1939-04-07 & Yes\\
Page & Earle Page & Country (Coalition) & 1939-04-07 & 1939-04-26 & No\\
\addlinespace
Menzies 1 & Robert Menzies & United Australia (Coalition) & 1939-04-26 & 1941-08-28 & No\\
Fadden & Arthur Fadden & Country (Coalition) & 1941-08-28 & 1941-10-07 & No\\
Curtin & John Curtin & Labor & 1941-10-07 & 1945-07-05 & Yes\\
Forde & Frank Forde & Labor & 1945-07-06 & 1945-07-13 & No\\
Chifley & Ben Chifley & Labor & 1945-07-13 & 1949-12-19 & No\\
\addlinespace
Menzies 2 & Robert Menzies & Liberal (Coalition) & 1949-12-19 & 1966-01-26 & No\\
Holt & Harold Holt & Liberal (Coalition) & 1966-01-26 & 1967-12-19 & Yes\\
McEwen & John McEwen & Country (Coalition) & 1967-12-19 & 1968-01-10 & No\\
Gorton & John Gorton & Liberal (Coalition) & 1968-01-10 & 1971-03-10 & No\\
McMahon & William McMahon & Liberal (Coalition) & 1971-03-10 & 1972-12-05 & No\\
\addlinespace
Whitlam & Gough Whitlam & Labor & 1972-12-05 & 1975-11-11 & No\\
Fraser & Malcolm Fraser & Liberal (Coalition) & 1975-11-11 & 1983-03-11 & No\\
Hawke & Bob Hawke & Labor & 1983-03-11 & 1991-12-20 & No\\
Keating & Paul Keating & Labor & 1991-12-20 & 1996-03-11 & No\\
Howard & John Howard & Liberal (Coalition) & 1996-03-11 & 2007-12-03 & No\\
\addlinespace
Rudd 1 & Kevin Rudd & Labor & 2007-12-03 & 2010-06-24 & No\\
Gillard & Julia Gillard & Labor & 2010-06-24 & 2013-06-27 & No\\
Rudd 2 & Kevin Rudd & Labor & 2013-06-27 & 2013-09-18 & No\\
Abbott & Tony Abbott & Liberal (Coalition) & 2013-09-18 & 2015-09-15 & No\\
Turnbull & Malcolm Turnbull & Liberal (Coalition) & 2015-09-15 & 2018-08-24 & No\\
Morrison & Scott Morrison & Liberal (Coalition) & 2018-08-24 & NA & NA\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:elections}Elections}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{rll}
\toprule
year & electionDate & electionWinner\\
\midrule
1901 & 1901-03-29 & Non-labor\\
1903 & 1903-12-16 & Non-labor\\
1906 & 1906-12-12 & Non-labor\\
1910 & 1910-04-13 & Labor\\
1913 & 1913-05-31 & Non-labor\\
\addlinespace
1914 & 1914-09-05 & Labor\\
1917 & 1917-05-05 & Non-labor\\
1919 & 1919-12-13 & Non-labor\\
1922 & 1922-12-16 & Non-labor\\
1925 & 1925-11-14 & Non-labor\\
\addlinespace
1928 & 1928-11-17 & Non-labor\\
1929 & 1929-10-12 & Labor\\
1931 & 1931-12-19 & Non-labor\\
1934 & 1934-09-15 & Non-labor\\
1937 & 1937-10-23 & Non-labor\\
\addlinespace
1940 & 1940-09-21 & Non-labor\\
1943 & 1943-08-21 & Labor\\
1946 & 1946-09-28 & Labor\\
1949 & 1949-12-10 & Non-labor\\
1951 & 1951-08-28 & Non-labor\\
\addlinespace
1954 & 1954-05-29 & Non-labor\\
1955 & 1955-12-10 & Non-labor\\
1958 & 1958-11-22 & Non-labor\\
1961 & 1961-12-09 & Non-labor\\
1963 & 1963-11-30 & Non-labor\\
\addlinespace
1966 & 1966-11-26 & Non-labor\\
1969 & 1969-10-25 & Non-labor\\
1972 & 1972-12-02 & Labor\\
1974 & 1974-05-18 & Labor\\
1975 & 1975-12-13 & Non-labor\\
\addlinespace
1977 & 1977-12-10 & Non-labor\\
1980 & 1980-10-18 & Non-labor\\
1983 & 1983-03-05 & Labor\\
1984 & 1984-12-01 & Labor\\
1987 & 1987-07-11 & Labor\\
\addlinespace
1990 & 1990-03-24 & Labor\\
1993 & 1993-03-13 & Labor\\
1996 & 1996-03-02 & Non-labor\\
1998 & 1998-10-03 & Non-labor\\
2001 & 2001-11-10 & Non-labor\\
\addlinespace
2004 & 2004-10-09 & Non-labor\\
2007 & 2007-11-24 & Labor\\
2010 & 2010-08-21 & Labor\\
2013 & 2013-09-07 & Non-labor\\
2016 & 2016-07-02 & Non-labor\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:economics}Key economic events}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{ll}
\toprule
theDate & event\\
\midrule
1907-11-08 & Harvester case\\
1910-09-01 & Australian pound introduced (CHECK DATE)\\
1929-10-29 & Black Tuesday Stock Market Crash\\
1931-06-01 & Premiers' Plan (CHECK DATE)\\
1966-02-14 & Decimalisation\\
\addlinespace
1973-01-01 & Fred Gruen 25\% tariff cut (DATE IS WRONG)\\
1983-12-12 & Australian dollar is floated\\
1984-02-01 & Medicare establised\\
1987-10-19 & Black Monday Stock Market Crash\\
1991-02-10 & State Bank of South Australia collapse\\
\addlinespace
1990-08-27 & State Bank of Victoria collapse (CHECK DATE)\\
2000-07-01 & GST introduced\\
2008-09-15 & Lehman Brothers bankruptcy\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:others}Key other events}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{ll}
\toprule
theDate & event\\
\midrule
1899-10-11 & Second Boer War starts\\
1901-01-01 & Australia federated\\
1902-05-31 & Second Boer War ends\\
1914-07-28 & World War I starts\\
1918-11-11 & World War I ends\\
\addlinespace
1932-05-13 & Jack Lang dismissed as NSW Premier\\
1939-09-01 & World War II starts\\
1945-09-02 & World War II ends\\
1949-10-17 & Snowy Hydro construction begins\\
1956-11-22 & Melbourne Olympics\\
\addlinespace
1962-08-03 & Australia enters Vietnam War\\
1972-12-02 & Australia exits Vietnam War\\
1973-10-20 & White Australian Policy ended\\
1975-11-11 & The Dismissal\\
1992-06-03 & Mabo\\
\addlinespace
1996-12-23 & Wik decision\\
1996-03-28 & Port Arthur massacre\\
1999-09-20 & INTERFET deployment begins\\
2000-02-28 & INTERFET deployment ends\\
2000-09-15 & Sydney Olympics\\
\addlinespace
2001-09-11 & 9/11 attack\\
2002-10-12 & Bali bombings\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\title{The Effect of Events on Australian Parliamentary Discussion (1851--2017) \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris
Cochrane for their helpful suggestions. \textbf{Version as of}: 02
October 2018; \textbf{comments welcome}:
\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}.}  }

@@

\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Monica Alexander (University of Toronto) and Rohan Alexander (Australian National University)},
             pdfkeywords = {text analysis, politics, Australia},  
            pdftitle={The Effect of Events on Australian Parliamentary Discussion (1851--2017)},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

\noindent We systematically analyse how parliamentary discussion changes in
response to different types of events in Australian history. We first
compile a dataset of what was said in Australian state and federal
parliaments from the mid-1800s through to 2017 based on available public
records. We then use a structural text model to reduce the
dimensionality of the text and to impose prior knowledge such as
correlation between days and steady changes over time. Finally, we
consider the effect of various events using Bayesian hierarchical
Dirichlet regression. We find that: 1) elections are associated with
topic changes only when the party in power changes; 2) a change in
government can be associated with topic changes even if the party in
power does not change; 3) economic events, such as financial crises,
have less significant and persistent effects than other events such as
terrorist attacks. Our findings have implications for how we think about
the longer-term trajectory of government policymaking as the media cycle
becomes increasingly focused on the short-term.

@@

In this paper we examine text records of what was said in Australian
state and federal parliaments from the mid-1800s through to 2017. We use
the Structural Topic Model (STM) of \citet{RobertsStewartAiroldi2016}
for dimensionality reduction and to impose structure such as correlation
between days and changes over time. We then use Bayesian hierarchical
Dirichlet regression to examine changes at various types of events,
including: changes in government; changes in the political environment
(as defined by polling or other results); changes in economic
conditions; and other significant events (such as the 9/11 attacks or
the Bali bombings).

@@

Our paper applies a topic model to a dataset of larger-scale
parliamentary text records from multiple Australian parliaments. Our use
of Bayesian hierarchical Dirichlet regression allows us to construct a
counterfactual. Our work fits into a growing literature that considers
text as an input to more usual quantitative techniques, rather than
requiring separate analysis. While using text as data has well-known
shortcomings, it allows larger-scale analysis that would not be viable
using less-automated approaches and so it can identify patterns that may
otherwise be overlooked.

@@

Australian parliaments generally make their daily Hansard records
available online as PDFs and these are considered the official release.
Additionally, there is a more limited set of XML records available in
some cases.\footnote{Tim Sherratt makes these XML records available as a
  single download and also presents them in a website
  (\url{http://historichansard.net/}) that can be used to explore
  Commonwealth Hansard records from 1901 to 1980. Commonwealth XML
  records from 1998 to 2014 are available from Andrew Turpin's website,
  and from 2006 through to today from Open Australia's website. The
  records can also be downloaded from the Australian Hansard website.}
We detail the sources of our Hansard PDFs in \ref{hansardsources} and
Appendix \ref{examplehansardpage} provides an example of what a Hansard
PDF looks like. There are roughly 54,331 \textbf{{[}UPDATE{]}} days
worth of publicly available Hansard records across the state and federal
parliaments (Table \ref{tab:yearsusedtable}). Our data cleaning process
indicates concerns with a small number of PDFs and these are detailed in
Appendix \ref{knownhansardissues}.

@@

\caption{\label{tab:missingdays}Missing days}
\centering
\fontsize{12}{14}\selectfont
\begin{tabular}[t]{rrrrr}
\toprule
year & HoR PDFs                      & Senate sitting days           & HoR sitting days              & HoR difference\\
\midrule
1902 & 106 & 93 & 107 & 1\\
1908 & 93 & 84 & 91 & -2\\
1909 & 97 & 71 & 98 & 1\\
1918 & 87 & 68 & 86 & -1\\
1920 & 113 & 76 & 114 & 1\\
\addlinespace
1921 & 92 & 79 & 93 & 1\\
1934 & 36 & 22 & 35 & -1\\
1935 & 54 & 37 & 55 & 1\\
1942 & 44 & 36 & 45 & 1\\
1948 & 89 & 39 & 90 & 1\\
\addlinespace
1951 & 55 & 40 & 56 & 1\\
1955 & 53 & 36 & 52 & -1\\
1974 & 64 & 64 & 62 & -2\\
1985 & 65 & 74 & 66 & 1\\
1991 & 66 & 83 & 67 & 1\\
\addlinespace
1992 & 60 & 76 & 44 & -16\\
1993 & 47 & 53 & 46 & -1\\
1994 & 69 & 80 & 68 & -1\\
1995 & 71 & 78 & 70 & -1\\
1997 & 79 & 82 & 76 & -3\\
\addlinespace
1998 & 56 & 57 & 54 & -2\\
2000 & 71 & 71 & 73 & 2\\
2002 & 68 & 60 & 69 & 1\\
2003 & 74 & 64 & 75 & 1\\
2004 & 58 & 49 & 59 & 1\\
2012 & 63 & 57 & 67 & 4\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:governments}Change in governments}
\centering
\fontsize{12}{14}\selectfont
\begin{tabular}[t]{llllll}
\toprule
government & primeMinister & party & start & end & diedInOffice\\
\midrule
Barton & Edmund Barton & Protectionist & 1901-01-01 & 1903-09-24 & No\\
Deakin 1 & Alfred Deakin & Protectionist & 1903-09-24 & 1904-04-27 & No\\
Watson & Chris Watson & Labour & 1904-04-27 & 1904-08-18 & No\\
Reid & George Reid & Free Trade & 1904-08-18 & 1905-07-05 & No\\
Deakin 2 & Alfred Deakin & Protectionist & 1905-07-05 & 1908-11-13 & No\\
\addlinespace
Fisher 1 & Andrew Fisher & Labour & 1908-11-13 & 1909-06-02 & No\\
Deakin 3 & Alfred Deakin & Commonwealth Liberal & 1909-06-02 & 1910-04-29 & No\\
Fisher 2 & Andrew Fisher & Labor & 1910-04-29 & 1913-06-24 & No\\
Cook & Joseph Cook & Commonwealth Liberal & 1913-06-24 & 1914-09-17 & No\\
Fisher 3 & Andrew Fisher & Labor & 1914-09-17 & 1915-10-27 & No\\
\addlinespace
Hughes & Billy Hughes & Labor, National Labor and Nationalist & 1915-10-27 & 1923-02-09 & No\\
Bruce & Stanley Bruce & Nationalist (Coalition) & 1923-02-09 & 1929-10-22 & No\\
Scullin & James Scullin & Labor & 1929-10-22 & 1932-01-06 & No\\
Lyons & Joseph Lyons & United Australia (Coalition) & 1932-01-06 & 1939-04-07 & Yes\\
Page & Earle Page & Country (Coalition) & 1939-04-07 & 1939-04-26 & No\\
\addlinespace
Menzies 1 & Robert Menzies & United Australia (Coalition) & 1939-04-26 & 1941-08-28 & No\\
Fadden & Arthur Fadden & Country (Coalition) & 1941-08-28 & 1941-10-07 & No\\
Curtin & John Curtin & Labor & 1941-10-07 & 1945-07-05 & Yes\\
Forde & Frank Forde & Labor & 1945-07-06 & 1945-07-13 & No\\
Chifley & Ben Chifley & Labor & 1945-07-13 & 1949-12-19 & No\\
\addlinespace
Menzies 2 & Robert Menzies & Liberal (Coalition) & 1949-12-19 & 1966-01-26 & No\\
Holt & Harold Holt & Liberal (Coalition) & 1966-01-26 & 1967-12-19 & Yes\\
McEwen & John McEwen & Country (Coalition) & 1967-12-19 & 1968-01-10 & No\\
Gorton & John Gorton & Liberal (Coalition) & 1968-01-10 & 1971-03-10 & No\\
McMahon & William McMahon & Liberal (Coalition) & 1971-03-10 & 1972-12-05 & No\\
\addlinespace
Whitlam & Gough Whitlam & Labor & 1972-12-05 & 1975-11-11 & No\\
Fraser & Malcolm Fraser & Liberal (Coalition) & 1975-11-11 & 1983-03-11 & No\\
Hawke & Bob Hawke & Labor & 1983-03-11 & 1991-12-20 & No\\
Keating & Paul Keating & Labor & 1991-12-20 & 1996-03-11 & No\\
Howard & John Howard & Liberal (Coalition) & 1996-03-11 & 2007-12-03 & No\\
\addlinespace
Rudd 1 & Kevin Rudd & Labor & 2007-12-03 & 2010-06-24 & No\\
Gillard & Julia Gillard & Labor & 2010-06-24 & 2013-06-27 & No\\
Rudd 2 & Kevin Rudd & Labor & 2013-06-27 & 2013-09-18 & No\\
Abbott & Tony Abbott & Liberal (Coalition) & 2013-09-18 & 2015-09-15 & No\\
Turnbull & Malcolm Turnbull & Liberal (Coalition) & 2015-09-15 & 2018-08-24 & No\\
Morrison & Scott Morrison & Liberal (Coalition) & 2018-08-24 & NA & NA\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:elections}Elections}
\centering
\fontsize{12}{14}\selectfont
\begin{tabular}[t]{rll}
\toprule
year & electionDate & electionWinner\\
\midrule
1901 & 1901-03-29 & Non-labor\\
1903 & 1903-12-16 & Non-labor\\
1906 & 1906-12-12 & Non-labor\\
1910 & 1910-04-13 & Labor\\
1913 & 1913-05-31 & Non-labor\\
\addlinespace
1914 & 1914-09-05 & Labor\\
1917 & 1917-05-05 & Non-labor\\
1919 & 1919-12-13 & Non-labor\\
1922 & 1922-12-16 & Non-labor\\
1925 & 1925-11-14 & Non-labor\\
\addlinespace
1928 & 1928-11-17 & Non-labor\\
1929 & 1929-10-12 & Labor\\
1931 & 1931-12-19 & Non-labor\\
1934 & 1934-09-15 & Non-labor\\
1937 & 1937-10-23 & Non-labor\\
\addlinespace
1940 & 1940-09-21 & Non-labor\\
1943 & 1943-08-21 & Labor\\
1946 & 1946-09-28 & Labor\\
1949 & 1949-12-10 & Non-labor\\
1951 & 1951-08-28 & Non-labor\\
\addlinespace
1954 & 1954-05-29 & Non-labor\\
1955 & 1955-12-10 & Non-labor\\
1958 & 1958-11-22 & Non-labor\\
1961 & 1961-12-09 & Non-labor\\
1963 & 1963-11-30 & Non-labor\\
\addlinespace
1966 & 1966-11-26 & Non-labor\\
1969 & 1969-10-25 & Non-labor\\
1972 & 1972-12-02 & Labor\\
1974 & 1974-05-18 & Labor\\
1975 & 1975-12-13 & Non-labor\\
\addlinespace
1977 & 1977-12-10 & Non-labor\\
1980 & 1980-10-18 & Non-labor\\
1983 & 1983-03-05 & Labor\\
1984 & 1984-12-01 & Labor\\
1987 & 1987-07-11 & Labor\\
\addlinespace
1990 & 1990-03-24 & Labor\\
1993 & 1993-03-13 & Labor\\
1996 & 1996-03-02 & Non-labor\\
1998 & 1998-10-03 & Non-labor\\
2001 & 2001-11-10 & Non-labor\\
\addlinespace
2004 & 2004-10-09 & Non-labor\\
2007 & 2007-11-24 & Labor\\
2010 & 2010-08-21 & Labor\\
2013 & 2013-09-07 & Non-labor\\
2016 & 2016-07-02 & Non-labor\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:economics}Key economic events}
\centering
\fontsize{12}{14}\selectfont
\begin{tabular}[t]{ll}
\toprule
theDate & event\\
\midrule
1907-11-08 & Harvester case\\
1910-09-01 & Australian pound introduced (CHECK DATE)\\
1929-10-29 & Black Tuesday Stock Market Crash\\
1931-06-01 & Premiers' Plan (CHECK DATE)\\
1966-02-14 & Decimalisation\\
\addlinespace
1973-01-01 & Fred Gruen 25\% tariff cut (DATE IS WRONG)\\
1983-12-12 & Australian dollar is floated\\
1984-02-01 & Medicare establised\\
1987-10-19 & Black Monday Stock Market Crash\\
1991-02-10 & State Bank of South Australia collapse\\
\addlinespace
1990-08-27 & State Bank of Victoria collapse (CHECK DATE)\\
2000-07-01 & GST introduced\\
2008-09-15 & Lehman Brothers bankruptcy\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:others}Key other events}
\centering
\fontsize{12}{14}\selectfont
\begin{tabular}[t]{ll}
\toprule
theDate & event\\
\midrule
1899-10-11 & Second Boer War starts\\
1901-01-01 & Australia federated\\
1902-05-31 & Second Boer War ends\\
1914-07-28 & World War I starts\\
1918-11-11 & World War I ends\\
\addlinespace
1932-05-13 & Jack Lang dismissed as NSW Premier\\
1939-09-01 & World War II starts\\
1945-09-02 & World War II ends\\
1949-10-17 & Snowy Hydro construction begins\\
1956-11-22 & Melbourne Olympics\\
\addlinespace
1962-08-03 & Australia enters Vietnam War\\
1972-12-02 & Australia exits Vietnam War\\
1973-10-20 & White Australian Policy ended\\
1975-11-11 & The Dismissal\\
1992-06-03 & Mabo\\
\addlinespace
1996-12-23 & Wik decision\\
1996-03-28 & Port Arthur massacre\\
1999-09-20 & INTERFET deployment begins\\
2000-02-28 & INTERFET deployment ends\\
2000-09-15 & Sydney Olympics\\
\addlinespace
2001-09-11 & 9/11 attack\\
2002-10-12 & Bali bombings\\
\bottomrule
\end{tabular}
\end{table}
